Weather classification using Convolutional Neural Networks

### 2020-01-26 msc_english_contents.tex
Add some basic image classification stuff

\chapter{Tasks}
What has been done when solving these tasks/history/formal definition
\section{Image classification}
Cover some results on similar datasets and their approaches, maybe show that old SIFT/HOG features don't really work vs CNN
\subsection{Transfer learning}
\subsection{ResNet}
\subsection{EfficientNet}
\section{Object detection}
Based on what is going to be detected, maybe text?
\section{Paragraph captioning}
Assuming we are doing this
\section{Multi task learning}
Cover some examples of MTL in Computer Vision

>>>>

\chapter{Tasks}
What has been done when solving these tasks/history/formal definition
\section{Image classification}
Image classification is one of the basic modern computer vision problems, where the goal is to create a model that can classify an input image into one of a set of pre-defined classes. Prior to the popularization of applying large Convolutional Neural Networks for this task, the most successful way of solving the problem was to use some algorithm for finding feature descriptors in a set of images and then training a linear classifier, like a Support Vector Machine over a Visual Bag of Words representation of the images. These days nearly all approaches are based on using deep CNNs.
\subsection{ImageNet}
ImageNet  \citep{imagenet}  is perhaps the most significant dataset for image classification and especially the ImageNet Large Scale Visual Recognition Challenge \citep{ILSVRC}, which is a challenge for a collection of 1000 classes from the ImageNet dataset for image classification using 1.2 million training and 150 thousand test images of the entire ImageNet dataset.

ImageNet  \citep{imagenet}  is perhaps the most significant dataset for image classification and especially the ImageNet Challenge \citep{ILSVRC}, which is a challenge for a collection of 1000 classes from the ImageNet dataset for image classification using 1.2 million training and 150 thousand test images of the entire ImageNet dataset. In 2012 the winning model, AlexNet \citep{alexNet}, showed that it was possible to train a deep CNNs efficiently using GPUs. Since 2012 all top-performing models showed some new improvements on how to create the most performant network architecture, for example, VGGNet from the year 2014 and ResNet \citep{resNet} from 2015, both of which have been popular models to use for Transfer Learning since.

Human accuracy on the ImageNet challenge is about 5.1\% \citep{imageNet_summary}, and ResNet achieves a top-5 error rate of 3.57\% \citep{resNet} and newer architectures even lower, but this still does not mean that image classification is a solved problem. The human performance experiment found that many of the human errors are caused by not having expert information in, for example, identifying animal species or not even being aware of the existence of a class \citep{imageNet_summary}. ObjectNet \citep{objectNet} is a dataset designed to test image classifiers with a focus on their generalizability. It contains many classes that also exist in the ImageNet dataset. However, they are in unexpected locations or have an unexpected pose, causing the high accuracy image classifiers trained on ImageNet experience a 40-45\% accuracy drop when evaluating them on the ObjectNet images of classes shared between ImageNet and ObjectNet. This kind of adjustment is relatively easy for a human, and it shows that while the classifiers are good, they are by no means perfect.
\subsection{Transfer learning}
\subsection{ResNet}
\subsection{EfficientNet}
\section{Object detection}
Based on what is going to be detected, maybe text?
\section{Paragraph captioning}
Assuming we are doing this
\section{Multi task learning}
Cover some examples of MTL in Computer Vision
